Analysis

### 2025-06-11 production/prod_analysis-fix-t5.Rmd
change colors corrplot

@@

grid::grid.text("Source: own elaboration with data 
from ELSOC 2023 (n = 1322)", x = 0.01, y = 0.05, just = "left", gp = grid::gpar(fontsize = 12, col = "black"))

>>>>

  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",

@@

grid::grid.text("Source: own elaboration with data from ELSOC 2023 (n = 1322)", x = 0.99, y = 0.1, just = "right", gp = grid::gpar(fontsize = 12, col = "black"))
